DS 710
R Programming Assignment
Homework 1: Share text file containing R code
For each of the following, copy your R code and the output (and your written response, for part 1.8) into a .r, .txt, .doc, .docx, or .rmd document. Submit your finished document to GitHub.

1.0 Open R. The first line of text in the console window tells you which version of R you are running (this should be version 3.1.2). Copy this line of text into a document, to verify that you've installed the correct version.

R version 3.1.2 (2014-10-31) -- "Pumpkin Helmet"

1.1 Calculate the cube root of 2015, as follows:
2015^(1/3)

```{r} 2015^(1/3)```

`r 2015^(1/3)`

1.2 Find the absolute value of 5.7 minus 6.8 divided by .58:
abs(5.7-6.8)/.58

```{r} abs(5.7-6.8)/.58```

`r abs(5.7-6.8)/.58`

1.3 Create a list of integers from 1 to 12 and call it a:
a = 1:12
a #(this will print a, so you can paste it into your homework; do this each time)

```{r} a = 1:12```

`r a = 1:12
a`

1.4 Create a sequence of odd numbers from 1 to 11:
b = c(1, 3, 5, 7, 9, 11)
b

```{r} b = c(1, 3, 5, 7, 9, 11)```

`r b = c(1, 3, 5, 7, 9, 11)
b`

1.5 Create the same sequence in another way:
c = seq(1,11, 2)
c

```{r} c = seq(1,11,2)```

`r c = seq(1,11,2)
c`

1.6 Take the natural log (ln) of a. (Note that this is done to the entire vector called a.)
ln.a = log(a)
ln.a

```{r} log(a)```

`r log(a)`

1.7 Compute the squares of the odd numbers from 1 to 11.

```{r} seq(1,11,2)^2```

`r seq(1,11,2)^2` 

1.8 Use ?sd to view the help file for the sd function. What does it do?
Standard Deviation

1.9. Create a variable Name that contains your first name. Because your name is a character string, not a number, you will need to put it in quotes so that R knows not to go looking for a variable with that name:
Name = "Susan"
Then type
paste("My name is", Name)

```{r} Name = "Paul"
paste("My name is", Name)```

`r Name = "Paul"
paste("My name is", Name)`

1.10 When you shut down R, R will ask if you want to save the workspace image. Always choose no. 
(Saving the workspace image means saving in memory any variables you have defined. It does not save the code you wrote - you need to save your code in a .r file, or script, for this. Saving your variables can be confusing: If you later write another function thats supposed to use, say, the name of a company, stored in the variable Name - but forget to initialize it, normally R would give you an error message that you could use to figure out your mistake. But if you save the workspace image, then R won't give an error message. It will just use the stored value of Name - but thats your name, not the company name. This produces a bug that can be much harder to track down.)
