---
output: word_document
---

# Assignment 9

###1

```{r }
#1a.
d <- read.csv('usnews_clean.csv')
head(d)

#1b
summary(d$Graduation.rate)
hist(d$Graduation.rate)
boxplot(d$Graduation.rate)

d$College.Name[which(d$Graduation.rate > 100)]
d$Graduation.rate[which(d$Graduation.rate > 100)] = NA

#1c.
m <- aggregate(d$Pct.alumni.who.donate, by=list(d$Public.private.cat), FUN=mean, na.rm=TRUE)
names(m) = c('Type', 'Mean')
m

#1d.
t.test(d$Pct.alumni.who.donate ~ d$Public.private.cat)

#1e.
write.csv(d, file='usnews_r.csv', quote=FALSE, row.names=FALSE)
```

###1b.
The graduation rate for Cazenovia College was over 100%. This entry was converted to NA.

###1d.
We have enough evidence to reject the null hypothesis. In other words, it appears the means are statistically different. As such, it appears that whether one graduated from a public vs. private university is associated with whether one donates or not.

#2

```{r }
#2a.
d = read.csv('cps.csv')
plot(d$wage ~ d$educ)

#2b.
model = lm(d$wage ~ d$educ)
model
par(mfrow=c(2,2))
plot(model)

#2c.
d$time <- 1 / d$wage

#2d.
par(mfrow=c(1,1))
plot(d$time ~ d$educ)

#2e.
model = lm(d$time ~ d$educ)
abline(model, col='red')
summary(model)

#2f.
par(mfrow=c(2,2))
plot(model)
d$time[c(216,507, 518)] <- NA
model = lm(d$time ~ d$educ, na.action=na.exclude)
summary(model)
```

###2a. 
It apppears there is a positive relationship between wages and education but is sightly hard to tell to do how "zoomed in" the plot is.

###2b.
Without tranforming, we are missing some of the upper values of wages.

###2d.
The relationship between time and education is negative.

###2e.
Yes, I am happy with my decision to pursue a master's degree. Besides the enjoyment of the subject matter, it appears as one furthers education the time it takes to make \$1 goes down.

###2f.
The outliers appear to be rows 216, 507, and 518. After I remove them, the relationship is more significant. We now how stronger evidence that time is negatively associated with education.
